Interpretable Machine Learning

### 2021-07-05 chunks/story-wines.Rmd
adds some formulas

@@

1. Measure model error on test data
1. Shuffle feature of interest
1. Measure model error again
1. Compute difference or ratio

@@

```{r,  out.width = '72%'}
knitr::include_graphics("../images/pdp.gif")
```

@@

H-Statistic tells us how much of the effect of two is due to interactions.

```{r}
ntrct = Interaction$new(pred, feature = "alcohol")
plot(ntrct, ncols = 4)
```

>>>>

$$MAE(y,f(X)) = abs(y - f(X))$$

@@

1. Measure model error on test data (e.g. MAE)
1. Permute feature of interest
1. Measure model error again
1. Compute difference or ratio

@@

```{r,  out.width = '50%'}
knitr::include_graphics("../images/pdp.gif")
```

$$PDP(x) = \frac{1}{n} \sum_{i=1}^n f(x, x_C^{(i)})$$

@@

H-Statistic tells us how much of the effect of two is due to interactions: $H^2_{jk}= \frac{\sum_{i=1}^n\left[PD_{jk}(x^{(i)})-PD_j(x^{(i)})-PD_k(x^{(i)})\right]^2}{\sum_{i=1}^n{PD}^2_{jk}(x^{(i)})}$

```{r, out.width = "80%"}
ntrct = Interaction$new(pred, feature = "alcohol")
plot(ntrct, ncols = 4)
```
